RJObject Paper

### 2014-06-11 Documents/Paper/ms.tex
Talking about the oscillations

The sampling distribution (probability distribution for the data given the
parameters) is a normal (gaussian) distribution with mean zero and standard
deviation $\sigma$, applied independently to each data point:
\begin{eqnarray}
y_i | N, \{A_i\}, \{T_i\}, \{\phi_i\} \sim
\mathcal{N}\left(\mu(t_i), \sigma^2\right).
\end{eqnarray}
The simulated data is shown in Figure~\ref{fig:sinewave_data}.

@@

\section{``Transit'' Example}

>>>>

The sampling distribution (probability distribution for the data given the
parameters) is a normal (gaussian) distribution with mean zero and standard
deviation $\sigma$, applied independently to each data point:
\begin{eqnarray}
y_i | N, \{A_i\}, \{T_i\}, \{\phi_i\} \sim
\mathcal{N}\left(\mu(t_i), \sigma^2\right).
\end{eqnarray}
We simulated some data based on the assumption $N=2$.
The simulated data is shown in Figure~\ref{fig:sinewave_data}, and shows a
large, low period oscillation with a smaller, much faster oscillation
superimposed. The noise level is such that the fast oscillation is difficult
to detect.

@@

%\section{``Transit'' Example}
